Automated Reasoning of Relational properties using \\ Abstact Conflict Driven Clause Learning

### 2016-09-22 deductions.tex
deductions

Overapproximating.
\subsection{Forward Iteration Strategy}

@@

\subsection{Chaotic Iteration Strategy}

>>>>

Overapproximating.

begin{figure}[t]
\tiny
\begin{tabular}{l|l}
\hline
Main Module & Interface Functions \\
\hline
\begin{lstlisting}
int main() {
 unsigned x, y;
 __CPROVER_assume(x==y);
 x++;
 assert(x==y+1);
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
$cond#19 == (x#16 == y#18)
$guard#20 == ($cond#19 && $guard#0)
x#20 == 1u + x#16
x#20 == 1u + y#18 || !$guard#20
$guard#0 == TRUE
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{C Program ad its corresponding SSA}
\label{sw-ssa}
\end{figure}

\subsection{Forward Iteration Strategy}
For forward iteration on Figure~\ref{sw-ssa}, we need atleast 
one decision to deduce BOTTOM and prove safety. The deduction 
happens from right to left in forward iteration strategy.

The initialization of live variable and subsequent update depends on the iteration strategy.

@@

\subsection{Chaotic Iteration Strategy}  
The set of octagonal equilities corresponding to Figurei~\ref{sw-ssa}
is shown below. For chaotic, no decision is required to deduce BOTTOM.
x#20 > 1                                                                      
-x20 - y18 < -2                                                               
-x16 - x20 < -2                                                               
y18 - x20 < 0                                                                 
x16 - x20 < 0                                                                 
y18 > 0                                                                       
x16 > 0                                                                       
-x20 - y18 < 0                                                                
x16 + y18 > 1                                                                 
y18 - x16 < 1                                                                 
x20 - y18 < 2                                                                 
x16 - y18 < 1                                                                 
cond19                                                                        
x16 + y18 > 0                                                                 
guard20                                                                       
guard0                                                                        
x16 + x20 > 0                                                                 
x20 - x16 < 2
